Title Goes Here

### 2017-09-19 analysis/paper/paper.Rmd
what does word2vec do?

>>>>

```{r}
library(ldatuning)
result <- FindTopicsNumber(
  general_reduced_dtm,
  topics = seq(from = 2, to = 100, by = 2),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = list(seed = 77),
  mc.cores = 2L,
  verbose = TRUE
)

knitr::kable(result)
FindTopicsNumber_plot(result)
```

### 2017-09-19 analysis/paper/saa2018_general_sessions_word2vec.Rmd
what does word2vec do?

>>>>

```{r}
library(wordVectors)
library(magrittr)
library(stringr)

# Write abstracts out to text files
lapply(1:length(general_2018_papers$Abstract),
     function(i) write.table(tolower(str_trim(general_2018_papers$Abstract[i])),
                  file = paste0("abstracts/", general_2018_papers$`Abstract Id`[i], ".txt"),
                  quote = FALSE, 
                  row.names = FALSE,
                  col.names = FALSE))

length(list.files("abstracts/")) #178

prep_word2vec(origin = "abstracts/",
              destination = "abstracts/abstracts.txt",
              lowercase = TRUE,
              bundle_ngrams = 2)

model = train_word2vec("abstracts/abstracts.txt","abstracts/abstracts.bin",
                       vectors=200,
                       threads=4,
                       window=12,
                       iter=5,
                       negative_samples=0)

# model = read.vectors("cookbook_vectors.bin")

plot(model,perplexity=50)

set.seed(10)
centers = 50
clustering = kmeans(model,
                    centers = centers,
                    iter.max = 40)

sapply(sample(1:centers,10),function(n) {
  names(clustering$cluster[clustering$cluster==n][1:10])
})

```{r}
library(stringr)
library(text2vec)

itn <- map(general_2018_papers$Abstract, ~itoken(.x))

it = itoken(general_2018_papers$Abstract, progressbar = FALSE)
v = create_vocabulary(it) %>% prune_vocabulary(doc_proportion_max = 0.1, term_count_min = 5)
vectorizer = vocab_vectorizer(v)

# Jaccard similarity
# they will be in the same space because we use same vectorizer
# hash_vectorizer will also work fine
dtm1 = create_dtm(it1, vectorizer)

dtm2 = create_dtm(it2, vectorizer)

# Once we have representation of documents in vector space we are almost done. One thing remains - call sim2():

d1_d2_jac_sim = sim2(dtm1, dtm2, method = "jaccard", norm = "none")
# Check result:

dim(d1_d2_jac_sim)
## [1] 300 200
d1_d2_jac_sim[1:2, 1:5]
```

```{r}
library(stringr)
library(text2vec)
data("movie_review")
# select 500 rows for faster running times
movie_review = movie_review[1:500, ]
prep_fun = function(x) {
  x %>% 
    # make text lower case
    str_to_lower %>% 
    # remove non-alphanumeric symbols
    str_replace_all("[^[:alnum:]]", " ") %>% 
    # collapse multiple spaces
    str_replace_all("\\s+", " ")
}
movie_review$review_clean = prep_fun(movie_review$review)

doc_set_1 = movie_review[1:300, ]
it1 = itoken(doc_set_1$review_clean, progressbar = FALSE)

# specially take different number of docs in second set
doc_set_2 = movie_review[301:500, ]
it2 = itoken(doc_set_2$review_clean, progressbar = FALSE)

it = itoken(movie_review$review_clean, progressbar = FALSE)
v = create_vocabulary(it) %>% prune_vocabulary(doc_proportion_max = 0.1, term_count_min = 5)
vectorizer = vocab_vectorizer(v)

# Jaccard similarity
# they will be in the same space because we use same vectorizer
# hash_vectorizer will also work fine
dtm1 = create_dtm(it1, vectorizer)
dim(dtm1)
## [1]  300 2338
dtm2 = create_dtm(it2, vectorizer)
dim(dtm2)
## [1]  200 2338
# Once we have representation of documents in vector space we are almost done. One thing remains - call sim2():

d1_d2_jac_sim = sim2(dtm1, dtm2, method = "jaccard", norm = "none")
# Check result:

dim(d1_d2_jac_sim)
## [1] 300 200
d1_d2_jac_sim[1:2, 1:5]
